Working Title - CUT Research Paper

### 2019-04-15 CUT/paper.tex
literature review on reference material in exams

%\subsection{Frequency}
%can include takehome

>>>>

Another fundamental decision an instructor needs to make when designing an exam is whether or not they will allow students to make use of reference material during the exam. Perhaps the most common decision taken is to not allow reference material of any sort during an exam, the so-called Closed Book exam. On the other end of the reference material permissiveness spectrum is the Open Book exam. In an Open Book exam, students are permitted to use the primary reference material for the course, usually the recommended course textbook but alternatively all course notes may be permitted. For the purpose of our discussion an Open Book exam will be defined by the unmitigated allowance of a reference text where students can expect to find the answer to any reasonable basic fact about the subject they may need for an exam. Another option exists in the middle between Closed and Open Book exams. This option is what we will call Cheatsheet exams. In a Cheatsheet exam students are allowed to prepare a restricted set of notes to bring to the exam. Usually these notes are allowed to have any content the student may want on them, but with space and formatting restrictions which allow the notes they carry in to have significantly more compact information than an Open Book exam. Comparing the efficacy of Open versus Closed Book exams in the literature has led to mixed results.
On the positive side for Open Book exams, it has been shown that they lead to significantly lower test anxiety and stress among students leading up to the exam TODOCITE(Broyles, Cyr, and Korsen). This reduction in tension is hypothesized to lead to better study habits, such as focusing on understanding over rote memorization. It was found by (TODOCITE Weber, McBee and Krebs) that there are slight gains in student performance on Open Book exams over Closed Book exams. They also corroborate the findings of (Broyles, Cyr, and Korsen) that student test anxiety is reduced in an Open Book exam setting. 
A study of the empirical literature on Open Book exams conducted by TODOCITE (Theophilides and Dionysiou) supports the assertions that Open Book exams lead to lower test anxiety, and less focus on memorization over understanding. But their study also shows that Open Book examinations do not lead to higher test scores, in particular where critical-thinking questions are concerned. The findings of TODOCITE (Agarwal et al.) are even more lukewarm. They find that the effect of testing on student retention is equal between Open Book and Closed Book exams. Separate studies by TODOCITE (Ioannidou) and (Boniface) found that student reliance on their permitted notes during an Open Book exam correlated with lower test scores. The findings of Ioannidou further indicate that critical-thinking questions are not effected with any statistical significance by the variable of whether an exam is Open or Closed Book. Moore and Jensen) TODOCITE found that Open Book exams diminish long term retention of material among Biology students, and promote shallow-learning study strategies. The results of TODOCITE (Heijne-Penninga) support these findings, indicating that Closed Book exams do a better job of promoting deep-learning strategies among students than Open Book Exams.
